---
title: "data-modeling"
format: html
editor_options: 
  chunk_output_type: console
author: Liz Peterson
date: 4-9-25
---

```{r}
library(tidyverse)
library(here)
```

```{r}
snow_survey <- read.csv(here('ASDN_csv','ASDN_Snow_survey.csv'))
site <- read.csv(here('ASDN_csv','site.csv'))
species <- read.csv(here('ASDN_csv','species.csv'))
color_band_code <- read.csv(here('ASDN_csv','color_band_code.csv'))
personnel <- read.csv(here('ASDN_csv','personnel.csv'))
```

```{r}
glimpse(snow_survey)
glimpse(site)
glimpse(species)
glimpse(color_band_code)
glimpse(personnel)
```


```{sql}
CREATE TABLE Place (
    Code TEXT PRIMARY KEY,
    Location TEXT,
    Plot TEXT,
    Site TEXT
);

CREATE TABLE Observers (
    ID INTEGER PRIMARY KEY
    Observer TEXT UNIQUE
);

CREATE TABLE Survey (
    Survey TEXT PRIMARY KEY,
    Year INTEGER NOT NULL,
    Date DATE NOT NULL
    Plot TEXT NOT NULL,
    Snow_cover REAL CHECK (Snow_cover BETWEEN 0 and 100),
    Water_cover REAL CHECK (Water_cover BETWEEN 0 and 100),
    Land_cover REAL CHECK (Land_cover BETWEEN 0 and 100),
    Total_cover INTEGER CHECK (Total_cover = 100),
    Notes TEXT
    Observer_ID INTEGER
    Site_ID TEXT
);

CREATE TABLE Personnel (
    Abbreviation TEXT PRIMARY KEY,
    Name TEXT NOT NULL UNIQUE
    Observer_ID INTEGER
);
```

I am definitely interested in discussing the assignment further in class - I mostly just tried to incorporate as many variables as possible from each csv. I knew that I wanted to make sure that the cover values were within the ranges we defined in class, and specifically that the Total cover was equal to 100. I wanted to connect the personnel and observers tables, as well as the Place and the Survey tables. 
